---
title: "Diamonds"
author: "Awatef Alshehri"
date: "1/20/2022"
output: html_document
---

## Diamonds

Diamond is the highest quality stone and one of the materials that has a geometric and symmetrical structure. It is composed of pure carbon and nearly colorless. There are 4 C’s (Cut, Color, Clarity and Carat) that play a role in a diamond’s beauty and all together present how the diamond looks. They are the key components that impact diamond beauty, structure and make each stone uniqe. 

our objective is to explore the diamonds dataset and identify the features of diamonds in the given dataset. Moreover, to show some technical skill I learned in Data Scinces Immersive course such us GitHub, R, Python, and Command Line.   and not your nascent analytical skills.examine what of features affect the price of diamond. 

### Step 1: Installing the tidyverse packages

```{r}
install.packages("tidyverse")  # This package is common and used in data analysis.

```


```{r diamond}

library(tidyverse)
library(ggplot2)
# https://www.tidyverse.org/packages/

```

##### Core tidyverse: 

- ggplot2 : used for data visualization.
- tidyr   : used to get to tidy data (data with a consistent form).
- dplyr   : used for data manipulation.
- readr   : used to read rectangular data (like csv, tsv, and fwf)
- Purrr   : used to replace many "for loops" with code that is easier to write and more expressive.
- stringr : used for strings manipulation as easy as possible.
- forcats : used to solve common problems with factors

-----------------------------------------------------------------

### Step 2: Exploring the Dataset

```{r diamond}
Diam = diamonds   # identify the dataset
```


```{r diamond}
# To view the structure of the "diamonds" dataset

str(Diam)
```


```{r diamond}
# To view the top rows of "diamonds" dataset.

head(Diam)

```

```{r diamond}
# To view column names from diamond dataset

colnames(Diam)

```


```{r diamond}
#EDA 

dim(Diam)

# To have a view of the dataset structure

glimpse(Diam) 

```

-----------------------------------------------------------------

### Step 3: Cleaning Data

```{r diamond}

summary(Diam)

```


```{r diamond}

summarize(Diam, mean_carat = mean(carat))

```


----------------------------------------------------------------- 

### Step 4: Visualizing Data

#### A) Point plot:

```{r diamond}

ggplot(data = Diam, aes(x=carat, y = price, color = cut)) +
  geom_point()

```

```{r diamond}

ggplot(data = Diam, aes(x=depth, y = price, color = cut)) +
  geom_point()

```

#### B) Histograms plot:

```{r diamond}

ggplot(Diam, aes(price, fill = clarity)) +
  geom_histogram(bins = 30)
```

```{r diamond}

ggplot(Diam, aes(price, fill = color)) + 
  geom_histogram(binwidth = 30) + 
  facet_wrap(~ clarity, scale = "free_y")
```


#### C) Bar plot:

```{r diamond}
ggplot(data=Diam)+
  geom_bar(mapping = aes(x=cut , fill=cut))
```

```{r diamond}
# we creat stacked bar charts showing different classes

ggplot(data = Diam)+geom_bar(mapping=aes(x=cut,fill=clarity))

```





